% Copyright (C) 2011 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 


Why the laundromat?

I get more work done there

Than I do elsewhere.

}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 67: January 2011}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House in Midtown \textbar The People's Republic of Ames }
\end{center}


\newpage

Is winter over yet?

--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 January 2011

A new year opens \\
And a feeling, life is great \\
Occupies my mind

2 January 2011

The prospect of work \\
A dull cloud filling my mind \\
More vacation, please

3 January 2011

Piles of e-mail \\
An inexorable push \\ 
Of glaciers of words

\newpage

4 January 2011

A facturing dish \\
Slipping from my hands does not \\
Make it to freedom

5 January 2011

It's available \\
But can it be workable? \\
I hate this software

6 January 2011

This table feels weird \\
A spot, unusual seat \\
Not normally here

7 January 2011

Falling into space \\
Stare at the sky hard enough \\
And you start to float

8 January 2011

Let's watch a movie! \\
Which one? Theater? Stay home? \\
The choice is too much.

9 January 2011

Piles of reading \\
Are simultaneously \\
Joyous and stressful

10 January 2011

Damn the torpedos! \\
Full speed ahead! makes me sad \\
When will I say that?

\newpage

11 January 2011

With a bang! Awake. \\
What insidious person \\
Thought up alarm clocks?

12 January 2011

Newspapers stacked high \\
But seemingly never read \\
Who's printing this stuff?

13 January 2011

The doughnut craving \\
Is strongest in the morning \\
But comes anytime

14 January 2011

Roads naught but potholes \\
Asphalt skin cracked and broken \\
Bumpy ride indeed

15 January 2011

An idealized tree \\
One limb stretching to the sky \\
No leaves but wires

16 January 2011

I feel very warm \\
Yet I am not on fire \\
This robe is toasty

17 January 2011

Dark when I leave work \\
A winter storm is rolling \\
In the sky above


\newpage

18 January 2011

Templeton's dried out \\
Leaves a glorious smell that \\
I don't want to wash

19 January 2011

A commentator \\
Bloviating on TV \\
Twenty dollar word

20 January 2011

A life of leisure \\
Would it manage to fulfill? \\
Or be just boring?

21 January 2011

A few steps by foot \\
Cover miles on the train \\
Jump between cities

22 January 2011

A dark room, music \\
A wall of sound envelopes \\
The room closes in

23 January 2011

More wandering done \\
With the walking I've done here \\
My legs are talking

24 January 2011

Midnight, I'm awake \\
Here in the Amtrak parking \\
My car, though, is not


\newpage

25 January 2011

Gumption block: broken! \\
Pissed off enough, I march down \\
And buy a new car

26 January 2011

At night I gather \\
Food for the upcomming week \\
I like shopping late

27 January 2011

Cold and slushy ground \\
Squishing below feet frozen \\
A chill, cuts the air

28 January 2011

Blocking, non-blocking \\
Bits on the wire messy \\
Must kick, extra hard

29 January 2011

Microscopic view \\
Zeroed in, tunnel vision \\
Miss the big picture

30 January 2011

Feh, pizza again \\
The lack of gumption leads to \\
The easy dinner

31 January 2011

Snowpocalypse looms \\
At the store, people circle \\
Descending on food


\newpage

\begin{center}
\Large{Bonus Haiku}
\end{center}

A few weeks ago the author John Scalzi held a contest to get a minor
character in one of his upcoming novels to have your last name. The
contest was in the form of a haiku challenge, in one of four topics.
While I didn't win, I thought you might enjoy my entries:

Spider Monkey/Monkeys:

Never trust monkeys! \\
Oh Grandfather, why did I \\
Doubt your sage advice?

LASERS:

Light monotonic \\
Cohesion interrupted \\
Red mist of brain goo

Poor GPS directions:

Turn left. No! turn right! \\
Tiny map and grating voice--- \\
Sends me off a cliff!

Spontaneous Human Combustion:

Getting hot in here \\
You feel hot? No? I feel hot. \\
Flee! I'm on FIRE!



\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 980461}
\end{sideways}
\begin{sideways}
\Large{Ypsilanti MI 48198}
\end{sideways}


\end{document}


