% Copyright (C) 2012 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 

Outside the window

A room which does not exist

Seen only at night


}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 79: January 2012}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House by the Cloisters \textbar The People's Republic of Ames }
\end{center}


\newpage

I forgot to say something here last month, and only noticed
after printing out 40 of these things. Damn brain, be less
dum.

--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 January 2012

The bare cold new year \\
Expectant, all before us \\
Twelve months with promise

2 January 2012

Vow to eat oatmeal \\
More fiber and nutrition \\
These things fill my mind

3 January 2012

The bitter Hudson \\
A torrent of cold air blasts \\
Doors of a warm place

\newpage

4 January 2012

Accustomed rumble \\
At night, I hear the subway \\
Lulling me to sleep

5 January 2012

You fool many folks \\
With fake quote attributions. \\
Always works. -- Mark Twain

6 January 2012

Yearning for more sleep \\
Stumbling through the day, only \\
Wide awake at night

7 January 2012

Books of history \\
Of cities I no longer \\
Walk the streets of home

8 January 2012

A magic jar is \\
Necessary if you want \\
To store gumptions.

9 January 2012

Look at the toothbrush \\
``How did it get here'', I think. \\
Morning, too early

10 January 2012

The battery, weak \\
The laptop, warning me it's \\
Time to go to sleep


\newpage

11 January 2012

Regular craters \\
Containing a gooey mass \\
Waffles, so perfect

12 January 2012

Raspy hacking cough \\
Why haven't you left with the \\
Rest of my damn cold?

13 January 2012

With Winter so weak \\
I am done with it; crave Spring, \\
And the warmth it brings

14 January 2012

A river of air \\
Bracing, splashing off buildings \\
Birds swimming above

15 January 2012

Starting a big list: \\
``Things I Need To Get Rid Of" \\
At the top: Old Socks

16 January 2012

A list of errands \\
Running all over the place \\
Glad when it is done

17 January 2012

Wind monsters howling \\
Scream outside my apartment \\
Trying to break in


\newpage

18 January 2012

From the bookcase taunts \\
{\em Calculus Made Easy} --- and \\
What I've forgotten

19 January 2012

Slowest train ever \\
Trudging to 168 \\
Late to work today

20 January 2012

Standard Friday night \\
Movie playing, on the couch \\
Takeaway Chinese

21 January 2012

The ravine divides \\
The place where I am from the \\
Whiskey hot cocoa

22 January 2012

Productive cleaning \\
The apartment tidied up \\
Who the hell am I?

23 January 2012

Energy today \\
But will it last the whole week? \\
Only time will tell

24 January 2012

The dispatcher says \\
Stay there for a little bit--- \\
Stand clear of the doors

\newpage

25 January 2012

Like a tie-dye flag \\
Sharp color points in a row \\
Pins on a push board

26 January 2012

An old man razor \\
Is hard to find in this town \\
The blades --- everywhere

27 January 2012

How much paint? Or rust? \\
What is the fire escape \\
Really made up of?

28 January 2012

Window, just open \\
In sneaks the breeze, curtain flits \\
The wind is now seen

29 January 2012

Today I want cake \\
And yet there is no cake here \\
Where is the cake, man?

30 January 2012

In ephemera \\
Are stories that history \\
Needs to remember

31 January 2012

Glass of water full \\
Covers pulled back, pillow fluffed \\
Now it's time for bed


\newpage
\begin{center}{\bfseries Lentil Escarole Soup}\end{center}
Adapted from the {\em Post Punk Kitchen} website

You will need:

\begin{itemize}
    \item 2 tbsp olive oil
    \item 1 med. onion, finely chopped
    \item 2 garlic cloves, finely chopped
    \item 4 small carrots, chopped
    \item 1-1/2 c. green lentils, sorted and rinsed
    \item 1 14.5 oz can of peeled chopped tomotoes, low sodium
    \item 1 head escarole, washed completely, large stalky bits removed, chopped
\end{itemize}

{\em Note:} If you saved the liquid from a batch of Glorious Kale from
last month, use it for part of the water in this recipe.

Sweat the onions, garlic and carrots in olive oil until tender. Add the
lentils and tomatoes, and 9 cups of water (or sone). Bring to a boil,
then simmer for 45 minutes. Add the escarole and nutritional yeast, cook
for five or so more minutes.

Freezes well, tasy with croutons.

\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 250138}
\end{sideways}
\begin{sideways}
\Large{New York NY 10025}
\end{sideways}


\end{document}


