% Copyright (C) 2013 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 

Word probs? I feel bad.

I've got ninety-nine problems ---

A haiku's not one

}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 99: September 2013}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House by the Cloisters \textbar The People's Republic of Ames }
\end{center}


\newpage

Tomorrow is Halloween, so I figure I better sit down and print this out....

--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 September 2013

On Skype with my niece. \\
I pretend to be trapped in \\
The television

2 September 2013

An expressive mood \\
An early Monday morning \\
Want more fucking sleep

\newpage

3 September 2013

It's blended hollow \\
A mish-mash does not add up \\
Straight-up whiskey please

4 September 2013

Faith in obsession? \\
Or an obsession with faith? \\
Where was I going?

5 September 2013

A gift of chalk brings \\
Brightness to the sidewalk dull \\
With the city's dust

6 September 2013

Waking up early \\
I hatch a feeling, it grows \\
Make it a good day

7 September 2013

Dangling from a chain \\
High in the New Jersey sky \\
What was I thinking?

8 September 2013

Becoming hotter \\
A dull glow, faint, surfaces \\
Time to make French fries

9 September 2013

Natural belief \\
Supernatural reason \\
One wins in the end

\newpage

10 September 2013

In-situ hacking \\
No line input, sound system \\
Old school hold the mic

11 September 2013

A simple doodle \\
With iteration becomes \\
Queer infinity

12 September 2013

Dreams of carrot cake \\
Pretending that it's healthy \\
Doc is not amused

13 September 2013

In soup, there is truth \\
Sometimes the truth is hidden \\
Don't let it fool you

14 September 2013

What a thing it is \\
A brisk autumn morn, coffee \\
A walk through the park

15 September 2013

Your tag means nothing \\
If you want to impress me \\
Make art that's breathless

16 September 2013

My ancestral brain \\
Speaks of cabbage and butter \\
And some potatoes

\newpage

17 September 2013

Bust a gut laughing \\
A hurt all from happiness \\
Gasping for breath now

18 September 2013

Nobody told me \\
A cute guy in my building \\
Where's the damn memo?

19 September 2013

A fearless boardroom \\
Is just a room, a table \\
And a PR spin

20 September 2013

Fanatical pig \\
Swallowing all the quarters \\
Fat on pocket change

21 September 2013

Focus: nerding out \\
Staring at code until it \\
Finally makes sense

22 September 2013

Fair debauchery \\
Filling the bus with laughter \\
Wait for the revenge

23 September 2013

Grow insanity \\
Let it lie dormant, waiting  \\
For the seeds to sprout

\newpage

24 September 2013

Fuzzy bit of light \\
Cannot focus, in a blur \\
Is it a migraine?

25 September 2013

Pot of soup cooking \\
Smelling good when I get home \\
It's the best feeling

26 September 2013

Among the monkeys \\
There's no higher honor than \\
Going bananas

27 September 2013

Days without fire \\
May keep me in employment \\
But are just boring

28 September 2013

Powerless cement \\
Freshly poured, now autographed \\
Growing hard with time

29 September 2013

Off in the distance \\
Appearing before my eyes \\
The Sun, it's morning

30 September 2013

Mountains from molehills; \\
Sometimes an amazing climb \\
Starts from something small


\newpage

\begin{center}
    {\bfseries Goddamn Simple Apple Pie}
\end{center}

This is a fairly damn simple apple pie, especially if you use a pre-made crust. 
Get three or four baking apples --- I like Granny Smith, but you can use any 
that you like. A mix is nice too. You can really use any kind of apple, but
if you don't use a baking apple, you'll basically make an apple sauce pie, which
is fine too if that's what you like.

Peel, core and slice the apples into thin wedges. Slop on a bunch of sugar, a slightly
smaller bunch of cinnamon, and grate on some nutmeg. Stir this all up until all of
the apple slices are covered with sugar-cinnaman-nutmeg love. Put a bottom crust in
your pie pan, add the apples. Jiggle the pie pan until the apples are all settled in.
Put a crust on top, crimp shut, cut some vent holes and bake until the crust is all
golden brown and delicious. If you want an extra golden crust, brush with milk and 
sugar before you shove it in the oven. When done, let cool for 10 minutes, then eat.

If you don't have a pie pan, or just want to make a tart, you can make two out of
this. Cover a baking sheet with parchment paper (no parchment paper? Use alumninum
foil, I guess. No foil? {\em Sigh}. Spray the pan with some non-stick spray or
something). Lay a pie crust out, put the apples in the middle leaving about the
outer quarter diameter empty. Gently fold over the excess dough, crimping bits of
the dough together as you go. Do the same with the other crust, bake as above. 

\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 250138}
\end{sideways}
\begin{sideways}
\Large{New York NY 10025}
\end{sideways}


\end{document}


