% Copyright (C) 2012 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 

Windows wide open

A breeze, the quiet city

Night brings dreams of spring

}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 80: February 2012}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House by the Cloisters \textbar The People's Republic of Ames }
\end{center}


\newpage

While I love the back page recipes, I feel like I need to get out
and do some more photography. Next month, a photo. Then maybe
we'll switch it off and on a bit.

--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 February 2012

Feb--ru {\em ru} ar--y \\
Why is that r sitting there? \\
What good does it do?


\newpage

2 February 2012

The first step, doozy \\
Playing chicken with the train \\
Time for some flapjacks

3 February 2012

Where did I put that? \\
The book was sitting right there. \\
Now where did it go?

4 February 2012

A little moth flies \\
Lazily around the room \\
Go out the window

5 February 2012

I must go shopping \\
I keep looking in the fridge \\
Nothing good shows up

6 February 2012

Lazily floating \\
Fat clouds saunter through the sky \\
Heavy with shadows

7 February 2012

I still don't get trees. \\
Like long slender hands reaching \\
Up to get the sky

8 February 2012

The smell of almonds \\
Wrapped in a sugary glaze \\
Tempt every night

\newpage

9 February 2012

Consider numbers \\
And staggering at the count \\
Sit back, think letters

10 February 2012

You sir, with the hat \\
Like an old sea captain you \\
Command the sidewalk

11 February 2012

Glimpses of the past \\
Old zines, old scenes, long since past \\
Life a life in print

12 February 2012

An ode to Oatmeal: \\
Cheap, simple, easy, comfort. \\
In Breakfast there's Truth

13 February 2012

Ephermal smell \\
Paint wafting down the hall \\
Remodeling done

14 February 2012

I'm an idiot. \\
That book I was looking for? \\
Under some laundry.

15 February 2012

One ... two ... three ... four ... five \\
Numbers climb as seconds do \\
Six ... seven ... eight ... nine

\newpage

16 February 2012

The band in my head \\
From Weezer to Madonna \\
90s night tonight

17 February 2012

Why is that word that? \\
Who looked at a cup and said \\
``We shall utter ... `cup'"?

18 February 2012

Low fidelity \\
The songs playing in my head \\
Up way too early

19 February 2012

Little felty pads \\
On the legs of kitchen chairs \\
Keep the floors scratch free

20 February 2012

I have defeated \\
The mighty LDAP, slaying \\
Data left and right

21 February 2012

Fast, then slow, then fast \\
Tuesday feels like it's Thursday \\
Time warping at work

22 February 2012

New Jersey sirens \\
Wafting across the Hudson \\
Is it being bombed?


\newpage

23 February 2012

Winter's last breath, held --- \\
It's sigh, letting go, becomes \\
Roar of a new Spring

24 February 2012
 
Golden orb, bloody \\
Reliqishes all fluids \\
Moro orange for lunch

25 February 2012

Off the Atlantic \\
The winds rush to create swells \\
Rocking the ferry

26 February 2012

As boats, floating by \\
Yearn for distant lands; We sit \\
Grounded in the park

27 February 2012

Stone shoulders standing \\
Struggle to hold back brown earth \\
Grass tickles them both

28 February 2012

Pearlescent coat \\
Vainly tries to pretty up \\
The rat of the sky

29 February 2012

This day but four years \\
Screws my mental calendar \\
Why isn't it March?

\newpage
\begin{center}{\bfseries Quinoa with Roasted Red Peppers and Artichoke Hearts}\end{center}

I love this because I basically always have the stuff on hand to make it.

You will need:

\begin{itemize}
    \item 2 tbsp olive oil
    \item 1 med. onion, finely chopped
    \item 2 cups quinoa, rinsed
    \item 4 cups vegetable broth
    \item 1 large jar marinated artichoke hearts
    \item 1 large jar roasted red peppers
\end{itemize}

Sweat the onion in the olive oil, add the quinoa and vegetable broth. Bring to a boil
and simmer until the quinoa is done. While that is going on, drain the artichoke
hearts and roasted red peppers, saving the liquid and adding it to the quinoa. 
Chop the peppers and artichokes, add them to the cooked quinoa.

Tasty warm or cold, much better the next day.

\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 250138}
\end{sideways}
\begin{sideways}
\Large{New York NY 10025}
\end{sideways}


\end{document}


