% Copyright (C) 2011 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 

Where's all the snow at?

We haven't gotten much snow.

I feel cheated here

}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 78: December 2011}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House by the Cloisters \textbar The People's Republic of Ames }
\end{center}


\newpage



--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 December 2011

One month of work down \\
And still, nothing on fire \\
Doing pretty good

2 December 2011

Two more book cases \\
Should take the slack most nicely \\
Furniture run soon

3 December 2011

I like this table \\
Where I can work and look out \\
On the street below

\newpage

4 December 2011

In a dark corner \\
A book I knew I had hides \\
Until I clean up

5 December 2011

Over a month here \\
And I still haven't put up \\
Any posters yet

6 December 2011

That lamp's not broken! \\
It just needed adjustment. \\
And I feel crafty

7 December 2011

In bed with a book \\
A soft light glowing; I read \\
And then I doze off

8 December 2011

Rusty balcony \\
The fire escape is tempting \\
But I don't go out

9 December 2011

Why do I want plants? \\
I never take care of them, \\
And then they all die

10 December 2011

Almost the whole list \\
Except for the one thing that \\
I really did need

\newpage

11 December 2011

Say, who was that man, \\
Who first put the bomp in the \\
Bomp-she-bomp-she-bomp?

12 December 2011

Subway lady lies \\
The train two stations away \\
For fifteen minutes

13 Decembmer 2011

Glorious soup pot \\
A simmering tasty stew \\
Goes in my belly

14 December 2011

I found what I lost \\
When I put something away \\
Where it was to go

15 December 2011

This window, dirty \\
Is almost uncleanable \\
Without anti-grav

16 December 2011

The parties at a \\
Private university  \\
Can be pretty swank

17 December 2011

Ancient memories \\
FORTRAN 77 \\
It's out of my brain

\newpage

18 December 2011

Thwoomp thwoomp thwoomp thwoomp eetz \\
Boom eetz eetz eetz boom boom boom \\
Techno in my head

19 December 2011

Oranges blossoming \\
A faint mist, a citrus breeze \\
The peel is shredded

20 December 2011

The winter so far \\
Has been a pretty tame one \\
No snow makes me sad

21 December 2011

Random wisps of steam \\
Escape a grate in the street \\
The engine moves on

22 December 2011

Holiday party \\
Leftovers lead to grazing \\
Be still my waistline

23 December 2011

Two-thirty am \\
Is for still being awake \\
Not for awaking

24 December 2011

Toast! Let there be toast. \\
Some scrambled eggs would be nice. \\
Impromptu breakfast.

\newpage

25 December 2011

Best part of Christmas \\
Is fresh baked cinnamon rolls \\
Right from the oven

26 December 2011

So glad to be gone \\
But the few days away and \\
So glad to be back

27 December 2011

Where is the tea pot? \\
I know I just saw it there. \\
No tea is madness

28 December 2011

Three days work this week \\
Almost doesn't seem worth it \\
Hopefully it flies

29 December 2011

How the time does fly \\
Nearly the end of the year \\
When did that happen?

30 December 2011

Quiet radio \\
A song going through my head \\
Over and over

31 December 2011

Opening champagne \\
Is best done with a big knife \\
I learned that this year

\newpage
\begin{center}{\bfseries Glorious Kale}\end{center}
{\fontsize{10}{10}\selectfont
Taking a break from random photos to give you random recipes. Hope you enjoy.

You will need:

\begin{itemize}
    \item A giant pot, with a lid
    \item A steamer basket
    \item A heavy pan
    \item 2 lbs. of kale, cleaned and roughly chopped
    \item Various root vegetables (red potatoes, carrots, rutabaga, parsnips), prepped and 
          chunked up
    \item An onion
    \item Some oil to cook the onion
    \item Some sesame oil
\end{itemize}

In the pot put about an inch or so of water, put in the steamer basket and
get that going. Prep the root veggies, dump them in the steamer, sprinkle
some salt on them.

While that's steaming, chop up the onion and sweat it --- put some oil in the
pan on medium heat, dump in the onion, sprinkle on some salt. Cook until
soft and translucent, but not so hot that you hear a lot of sizzling and
the onion browns.

When the root vegetables feel like they're mostly done, drop in the kale,
sprinkle some salt on it, and put the lid back on. Cook for a few minutes,
just enough to cook the kale a bit but not so much that it becomes mush.

While that's happening, crank up the heat on the pan with the onion in
it and glug in some sesame oil. You want this hot. When it's there and
the kale is done, use some tongs to drop the kale into the hot oil. You
want to slightly sautee the kale, but keep it moving, and using the kale
to sweep up the oil and onions. Be careful, steamy vegetables and hot
oil sizzle {\em a lot}. When you're happy with the kale, put it on a
plate, put the steamed vegetables on top, glug on a little more sesame
oil, and enjoy.

Note: there will be liquid in the bottom of the steamer pot. Do {\em not}
throw that away, it's liquid awesome. My favorite use for it is in
soups; stay tuned next month for Lentil Escarole soup, which is a
perfect use for this.
}
\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 250138}
\end{sideways}
\begin{sideways}
\Large{New York NY 10025}
\end{sideways}


\end{document}


