% Copyright (C) 2012 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 

A time for warm things 

Pots of soup, hot chocolate 

And oven-fresh bread

}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 89: November 2012}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House by the Cloisters \textbar The People's Republic of Ames }
\end{center}


\newpage

I never buy a Christmas tree, but this year I did buy three big
bundles of pine trimmings and spread them on the sill under my
big living room window. It smells nice, and with a string of
lights strung through it looks nice and pretty.

--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 November 2012

There's another bus \\
Where it stops is uncertain --- \\
Certain frustration

2 November 2012

A hell of a week \\
The city feels strained but tough \\
A different vibe

\newpage

3 November 2012

The cold isn't bad \\
The constant sleepyness, though \\
Naps no longer fun

4 November 2012

Up here, some flooding \\
As the 207th Yard \\
Floods the 8th Ave Line

5 November 2012

After work, cleaning \\
Laundry, the dishes, tidy \\
Make the place look neat

6 November 2012

A new visitor \\
A quick blur, lightning shadow \\
It's a stupid mouse

7 November 2012

A helicopter \\
Shimmers in the sky, then leaves \\
Its blades an echo

8 November 2012

Video backlog \\
Handled with insomnia \\
I don't need to sleep

9 November 2012

Another weird word: \\
Towel: soft end expected \\
But hard `t' throws off

\newpage

10 November 2012

Neither and nor but \\
Not only yet but also \\
Whether for or so

11 November 2012

The Parks Department \\
Grinding away at broken trees \\
Disturbing my nap

12 November 2012

Sometimes I'm solo \\
In a vast crowd of people \\
There, but separate

13 November 2012

Climb with confidence \\
Don't dawdle on the staircase \\
Be bold and don't hold

14 November 2012

Salt of the Earth: good \\
Yet salting the earth is bad. \\
Who made this shit up?

15 November 2012

Cunning nonchalance \\
As I watch my dear mouse friend \\
Steal food from the trap

16 November 2012

It's the worst warning \\
Itching when you have to sneeze \\
Just in time: cover

\newpage

17 November 2012

Walking past often \\
For the first time I go in \\
What a lovely place

18 November 2012

A half lyric, stuck \\
Sing along until I can't \\
Then hum the next part

19 November 2012

A hall, dark, glitters \\
Lights glow as hundreds chit-chat \\
On a cold night, warmth

20 November 2012 

Walkways at airports \\
Are like real life speed boosters \\
Video game like

21 November 2012

The Bx7 \\
The final stop: Isham Street \\
Hate when it ends there

22 November 2012

Lord of the Rings Day \\
Too much food, too much movies \\
Not enough napping

23 November 2012

Productive today? \\
Why would I ever think that? \\
I am a moron.

\newpage

24 November 2012

Brief recognition \\
A face that I think I know. \\
It's not, I walk on

25 November 2012

I walk for leisure \\
The best way I can relax \\
Just step after step

26 November 2012

Gravity sure sucks \\
It's just keeping me down man \\
The Earth pulling me

27 November 2012

A vast twisty maze \\
Configuration jumbled \\
I just hate Java

28 November 2012

A railing of brass \\
Worn down by many decades \\
A million hands touch

29 November 2012

With a bang it falls \\
A stack of books left too long \\
Sliding to the floor

30 November 2012

Length of a mile \\
Warping here in the city \\
Long and short of it

\newpage

\begin{center}
{\bfseries Avocado Pie}
\end{center}

This is actually very tasty --- I was wary the first time I made it 
because I think of avocados only in savory dishes, so I was worries
I'd be making guacamole pie. But it's very good, a nice avocado taste
balanced with citrus and sweetness.

\begin{itemize}
    \item 2 ripe avocados
    \item 1 14 oz. can sweetened condensed milk
    \item Lemons and limes to make 1/2 cup juice
    \item Graham cracker crust
\end{itemize}

Juice the citrus into a bowl, scoop out the avocado into the juice
and stir to coat; this keeps the avocado from browning. Dump into
a blender or food processor, pulse a bit to break it up. Add the
sweetened condensed milk, pulse until you have a smooth, pudding-like consistency
Pour into the prepared crust, chill until set. 

The filling may darken a little bit. Good with whipped cream
on top.

\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 250138}
\end{sideways}
\begin{sideways}
\Large{New York NY 10025}
\end{sideways}


\end{document}


