% Copyright (C) 2011 Thomas L. Kula
% All Rights Reserved
%
% See the file LICENSE for license terms.
\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{fix-cm}
\usepackage{multirow}
\setlength{\paperwidth}{5.5in}
\setlength{\paperheight}{8.5in}
\setlength{\textheight}{7.45in}
\setlength{\topmargin}{-1.0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\textwidth}{4.0in}
\setlength{\parindent}{0in}
\setlength{\parskip}{3mm}
\usepackage[print]{booklet} \nofiles
\source{\magstep0}{5.5in}{8.5in}
\target{\magstep0}{11in}{8.5in}
\setpdftargetpages
\pagestyle{empty}
\begin{document}


\begin{center}
{\fontsize{36}{48}\selectfont \textsc{Haiku a Day }}
\end{center}

\vspace*{3.5cm}

{\fontsize{20}{40}\selectfont 


Sometimes it is strange

How a day can change one's mood

This, for the better


}

\vspace*{5.0cm}
\begin{center}
{\large{Issue 70: April 2011}} \\[5mm]
{\fontsize{8}{8}\selectfont  \textsc{ St. Joshua Norton Press }} \\[1mm]
{\fontsize{6}{6}\selectfont Mathom House in Midtown \textbar The People's Republic of Ames }
\end{center}


\newpage

So far this month the largest issue on my mind is getting a
head cold just was Spring really arrives. Feh. \\
--- Thomas

http://kula.tproa.net/had/ \\
kula@tproa.net

Download this and previous HADs at the website, so you can
print out your own (DIY, yeah!) or if you want me to send
you one, send me your address, and maybe a stamp if you
are feeling nice. Or send me something you've made ---
trades always appreciated, postcards are nice too.

\vfill

1 April 2011

Today, more stupid \\
The internet outshines \\
I hate this damn day

2 April 2011

On days like today \\
I just want the Talking Heads \\
Playing all day long

\newpage


3 April 2011

How are you purple? \\
Oh eggplant, what a strange hue \\
You flash on the shelf

4 April 2011

A cave never seen \\
In a mountain never climbed \\
Waterfall keeps guard

5 April 2011

Meetings too early \\
Fill with an infinite rage \\
There were no doughnuts

6 April 2011

Glowing rectangle \\
As an omen in the night \\
Advertising gas

7 April 2011

Old man, shouting phone \\
Recipe for fried chicken \\
I cross the street here

8 April 2011

Beacon calling out \\
``Hey, there's something tall right here!" \\
Flash red, stay away

9 April 2011

Ypsi universe \\
It's potholes all the way down \\
Holes have holes have holes

\newpage
10 April 2011

Walking, strut my stuff \\
One may think I'm so strung out \\
Blister in the Sun

11 April 2011

Oh glorious day \\
I revel in you, so good \\
This day makes me grin   

12 April 2011

Hate golden arches \\
But now, still craving french fries \\
I go to the store

13 April 2011

The mind, exhausted \\
Refused to go to sleep \\
Stab with a q-tip....

14 April 2011

Extinguisher sign \\
Yet no red can sits nearby \\
Shun fire safety

15 April 2011

Lots of whoas and raas \\
Something about bad romance \\
Leave my head, Gaga

16 April 2011

Car, special powers \\
Mission from God: save orphans \\
Brothers bring the blues

\newpage

17 April 2011

After a long nap \\
Energy for big cleaning \\
Okay, medium....

18 April 2011

Rambling about things \\
Hopefully my training talk \\
Made a bit of sense

19 April 2011

My ears still fuzzy \\
I did rock, and having rocked \\
I go home to sleep

20 April 2011

Going dodo's way \\
This technology, creaking \\
Still sputters along

21 April 2011

Shift: green, yellow, red \\
Idols in the sky, flashing \\
Governing our lives

22 April 2011

The little pothole \\
I walk past everyday \\
Keep up! You'll make it!

23 April 2011

A glorious day \\
The sky blue, a few clouds fly \\
High as my spirits

\newpage

24 April 2011

How restful, the nap  \\
The day calm, breezes lulling \\
Singing me to sleep

25 April 2011

Awaken early \\
Ready for the week ahead \\
What the hell is this?

26 April 2011

Morning haze glowing \\
Fades, growing calm, then bursting \\
As the Sun leaps up

27 April 2011

Staring does not lead \\
To a building falling down; \\
Mightily I try

28 April 2011

Half a day at work \\
Compliments of DTE \\
Can't keep the lights on

29 April 2011

Why thank you, Winter \\
For inflicting upon me \\
One last head cancer

30 April 2011

What color is this \\
The snot falling from my head \\
Unusual hue



\newpage

\begin{center}
{\Large Happy Fun Time Activity Page!} \\
\emph{Write your own haiku}

\vspace*{\fill}

(How did I not take any photos in April? Lame, right?)
\end{center}



\newpage

\thispagestyle{empty}
\vspace*{12cm}
\begin{sideways}
\Large{St. Joshua Norton Press}
\end{sideways}
\begin{sideways}
\Large{PO Box 980461}
\end{sideways}
\begin{sideways}
\Large{Ypsilanti MI 48198}
\end{sideways}


\end{document}


